---
output:
  word_document: default
---
<STYLE TYPE="text/css">
<!--
  td{
    font-family: Arial; 
    font-size: 4pt;
    padding:0px;
    cellpadding="0";
    cellspacing="0"
  }
  th {
    font-family: Arial; 
    font-size: 4pt;
    height: 20px;
    font-weight: bold;
    text-align: right;
    background-color: #ccccff;
  }
  table { 
    border-spacing: 0px;
    border-collapse: collapse;
  }
--->
</STYLE>

```{r, echo=FALSE}
rm(list=ls())

ls()
#Dimensions of the model
nAreas = 9 #Number of areas
nTime = 12 #Number of time steps - 12 months
nDays = c(31,28.25,31,30,31,30,31,31,30,31,30,31) #Number of days in each time-step (i.e., month)
nYear = 46 #Number of years in the study
nAges = 6 #the number of ages
nOrigin = 2 #Hatchery or wild 
nRun = 9 #Spring, Summer, Fall, Winter, 9 is the junk category with mixed runs and unknowns
nPred = 4 #The number of predators
nSex = 2 #1=Male, 2=Female
predAges = 25

#How many time-step are smolts allowed to stay in natal areas
smoltLAG = 2


#Names of the array dimensions
tNames = c('May', 'June', 'July', 'Aug', 'Sept', 'Oct', 'Nov', 'Dec', 'Jan', 'Feb', 'Mar','Apr')
originNames = c("Hatchery", "Wild")
runNames = c("Spring","Summmer","Fall","Winter","","","","","Other")
predNames = c("KW", "HS", "CSL", "SSL")
predNamesLong = c("Resident \n killer whales",'Harbor seals (000)', 'California \n sea lions (000)', 'Steller \n sea lions (000)')
sexNames = c("Male","Female")
areaNames = c("Cen.CA", "N.CA/OR", "Col.Riv.", "WA", "Sal.Sea", "WVI/N.BC", "SEAK", "WAK", "Bk.Box")
areaNamesLong = c("Central \n California", "NorCal \n Oregon", "Columbia \n River", "Washington", "Salish Sea", "WCVI \n NorBC", "Southeast \n Alaska", "Western \n Alaska", "Black box")

ptm <- proc.time()

runMCChain = FALSE
if(runMCChain == TRUE )
  nSim = 50
if(runMCChain ==FALSE)
  nSim = 1

mycv = c(0.2)
MC_Ncv = 0.15
MC_SELcv = 0.5
MC_FECcv = 0.5
MC_ALPHAcv = 0.2
MC_SMTLcv = 0.3
MC_CCONDcv = 0.2 #Fish condition, change in create_EChromta

simBC_cspjya = array(NA,c(length(mycv),nSim,nPred,nAreas,nYear,nAges))
simNC_cspjya = array(NA,c(length(mycv),nSim,nPred,nAreas,nYear,nAges))
simYears = c(41:46)

cvCnt = 1
for(icv in mycv){
  for(iSim in 1:nSim)
  {
    #Create the predator abundance by sex and age
    source("Create_Nphyis.r") #Abundance
  }
  cvCnt = cvCnt + 1
}  
```
#Appendix

##Population abundance

Table xx. Estimated killer whale abundance from 1970-2015
```{r, comment=NA, echo=FALSE, caption=""}
library(knitr)
library(xtable)
x = round(t(N_phy[1,5:8,]),0)
colnames(x) = areaNames[5:8]
rownames(x) = 1970:2015
print(x)
```


Table xx. Estimated harbor seal abundance from 1970-2015
```{r, comment=NA, echo=FALSE, caption=""}
library(knitr)
library(xtable)
x = round(t(N_phy[2,1:8,]),0)
colnames(x) = areaNames[1:8]
rownames(x) = 1970:2015
print(x)
```


Table xx. Estimated California sea lion abundance from 1970-2015
```{r, comment=NA, echo=FALSE, caption=""}
library(knitr)
library(xtable)
x = round(t(N_phy[3,1:8,]),0)
colnames(x) = areaNames[1:8]
rownames(x) = 1970:2015
print(x)
```

Table xx. Estimated Steller sea lion abundance from 1970-2015
```{r, comment=NA, echo=FALSE, caption=""}
library(knitr)
library(xtable)
x = round(t(N_phy[3,1:8,]),0)
colnames(x) = areaNames[1:8]
rownames(x) = 1970:2015
print(x)
```

##Age and sex ratio.

Table xx.  The estimated ratio of females in the predator populations during 2015.
```{r, comment=NA, echo=FALSE, caption=""}
mm = apply(N_phyis[,,46,,1],c(1,2), sum)
ff = apply(N_phyis[,,46,,2],c(1,2), sum)
xx = ff/(ff+mm)
colnames(xx) = areaNames
print(t(round(xx[,1:8],2)))
```

Table xx.  The estimated ratio of females in the predator populations during 2015.
```{r, comment=NA, echo=FALSE, caption=""}
aa = apply(N_phyis[,,46,,],c(1,3), sum)
aa = aa/rowSums(aa)
#colnames(xx) = areaNames
print(t(round(aa,2)))
```
